Writing a reproducible paper with Quarto

### 2023-02-17 paper.qmd
Update abstract

---
title: "Writing a reproducible paper with Quarto"
author: "Paul C. Bauer, Camille Landesvatter"
format: html
date: 'First version: 16 February, 2023<br>This version: `r format(Sys.time(), "%d %B, %Y")`'
abstract: 'The present paper provides a template to write a reproducible scientific paper with R Markdown and Pagedown.^[Based on an earlier R Markdown template that uses Latex and can be downloaded under https://osf.io/q395s [see @Bauer2018-dl].] Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing). Importantly, we also provide different CSS and HTML files that can be used to achieve a pdf output with the look of a "working paper". We are convinced that in the future there will be many improvements and developments with regards to RStudio, R markdown and Pagedown. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
tbl-cap-location: top
execute: 
  echo: false
  warning: false
  message: false
---

>>>>

---
title: "Writing a reproducible paper with Quarto"
author: "Paul C. Bauer, Camille Landesvatter"
format: html
date: 'First version: 16 February, 2023<br>This version: `r format(Sys.time(), "%d %B, %Y")`'
abstract: 'The present paper provides a template to write a reproducible scientific paper with Quarto. It is based on earlier Pagedown/RMarkdown templates that can be downloaded [here](https://osf.io/k8jhx/) [@Bauer2018-dl] and [here](https://osf.io/q395s) [@Bauer2021-dl]. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s?usp=sharing). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
tbl-cap-location: top
execute: 
  echo: false
  warning: false
  message: false
---
